---
title: "Plotting Exercise 2"
author: "MRC LMS"
date: "19/09/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

These exercises cover the sections of Plotting in R [PlottingInR](https://lmsbioinformatics.github.io/LMS_PlottingInR/course/PlotInR.html).



## Exercise 1

Please load the dateset **subset_GoT** from "Got_dataset/subset_GoT.csv" and use ggplot2 to 

(1) create a bar plot using subset_GoT\$social_status and see the number of characters are Highborn or Lowborn 

(2) a. asign colours according to whether they switched the allegiance (subset_GoT\$allegiance_switched)

    b. add argument **position=position_dodge()** in geom_bar() and see what happens

(3) use facet_wrap() to separate the figure according to their sex

(4) use facet_grid() to separate the figure according to their sex and occupation

(5) use facet_wrap() to separate the figure according to their sex and occupation and see the difference from the previous figure

(6) save the final figure as "pdf" file

[hint: use read.csv() function to load dataset]

```{r,echo=T,eval=F}
subset_GoT<-read.csv(file="Got_dataset/subset_GoT.csv")

head(subset_GoT)
```

```{r,echo=F,eval=F}

ggplot(subset_GoT,aes(x=social_status)) + 
  geom_bar()

ggplot(subset_GoT,aes(x=social_status,fill=allegiance_switched)) + 
  geom_bar()

ggplot(subset_GoT,aes(x=social_status,fill=allegiance_switched)) + 
  geom_bar(position=position_dodge())

ggplot(subset_GoT,aes(x=social_status,fill=allegiance_switched)) + 
  geom_bar()+facet_wrap(~sex)

ggplot(subset_GoT,aes(x=social_status,fill=allegiance_switched)) + 
  geom_bar()+facet_grid(sex~occupation)

ggplot(subset_GoT,aes(x=social_status,fill=allegiance_switched)) + 
  geom_bar()+facet_wrap(sex~occupation)


ggsave(file="final_figure.pdf")
```



