---
title: "Plotting Excercise 1"
author: "MRC LMS"
date: "19/09/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

These exercises cover the sections of Plotting in R [PlottingInR](https://lmsbioinformatics.github.io/LMS_Reproducible-R/r_course/introToR_Session1.html).



**Exercise 1**

Please load the dateset **mtcars** by calling data(mtcars) and use the base R graphics function to 

(1) create a scatter plot of mtcars$mpg VS mtcars$wt (x-axis = mpg and y-axis = wt). 

(2) change the labels for x axis and y axis

(3) change the colour of points to red and the the shape of points to "filled circle"

[hint: use data() function to load mtcars]

```{r,echo=T,eval=F}
data(mtcars)
head(mtcars)
plot(mtcars$mpg, mtcars$wt, main="scatter plot", xlab="MPG", ylab="WT",pch=16,col="red")

```



**Exercise 2**

Produce a plot like the one shown below. 
(Hint: you can use the matplot function to make the plots.) 

```{r,echo=FALSE}
x<-seq(-10,10,0.1) 
y<-sin(x) 
z<-cos(x) 
matplot(x,cbind(y,z),col=c("red","blue"),las=1,xlab="x",ylab="Sine(x) or Cosine(x)",lty=1:2,type="l")
```


**Exercise 3**
Check out the data in the data frame Loblolly (in the datasets package), on the growth of loblolly pine trees from different stocks. 
Create the following plot, or something similar 
(note that you will need to convert height from ft to m).

```{r,echo=FALSE}
ll.dat<-Loblolly 
ll.dat$height<-ll.dat$height*0.3048 
 
plot(height~age,type="n",xlab="Age (yr)",ylab="Height (m)",las=1,xlim=c(0,25),data=ll.dat) 
points(ll.dat$age[ll.dat$Seed==307],ll.dat$height[ll.dat$Seed==329],pch=1,col="red",type="o") 
points(ll.dat$age[ll.dat$Seed==311],ll.dat$height[ll.dat$Seed==307],pch=6,col="blue",type="o") 
points(ll.dat$age[ll.dat$Seed==311],ll.dat$height[ll.dat$Seed==311],pch=22,col="black",type="o") 
legend("topleft",legend=c(311,307,329),pch=c(1,6,22),col=c("red","blue","black"))
```


