---
title: "Plotting Answer 1"
author: "MRC LMS"
date: "19/09/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

These exercises cover the sections of Plotting in R [PlottingInR](https://lmsbioinformatics.github.io/LMS_PlottingInR/course/PlotInR.html).



## Exercise 1

Please load the dateset **mtcars** by calling data(mtcars) and use the base R graphics to 

(1) create a scatter plot of mtcars\$mpg VS mtcars\$wt (x-axis = mpg and y-axis = wt). 

(2) change the labels for x axis = "Miles/(US) gallon" and y axis = "Weight (1000 lbs)"

(3) add title = "scatter plot"

(4) change the colour of points to red and the the shape of points to "filled circle"

[hint: use data() function to load mtcars]

```{r,echo=T,eval=T}
data(mtcars)
head(mtcars)
plot(mtcars$mpg, mtcars$wt, main="scatter plot", xlab="Miles/(US) gallon", ylab="Weight (1000 lbs)",pch=16,col="red")
```


## Exercise 2

Please load the dateset **mtcars** by calling data(mtcars) and use the ggplot2 to 

(1) create a scatter plot of mtcars\$mpg VS mtcars\$wt (x-axis = mpg and y-axis = wt).

(2) change the labels for x axis = "Miles/(US) gallon" and y axis = "Weight (1000 lbs)"

(3) add title = "scatter plot"

(4) change the colour of points to red [hint: use col="red" when constructing aesthetic mappings]

```{r,echo=T,eval=F}
library(ggplot2)
g<- ggplot(mtcars, aes(x=mpg,y=wt,col="red"))+ geom_point()

# option 1
g + labs(x="Miles/(US) gallon",y="Weight (1000 lbs)",title="scatter plot")

# option 2
g + xlab("Miles/(US) gallon")+ylab("Weight (1000 lbs)") +
  ggtitle=("scatter plot"))
```


```{r,echo=F,eval=T}
#g<- ggplot(mtcars, aes(x=mpg,y=wt,col="red"))+ geom_point()
library(ggplot2)
# option 1
ggplot(mtcars, aes(x=mpg,y=wt,col="red"))+ geom_point() + labs(x="Miles/(US) gallon",y="Weight (1000 lbs)",title="scatter plot")

```

(5) a. what will happen if change the colour of points to mtcars\$am [hint: use col=am when constructing aesthetic mappings]

```{r,echo=T,eval=T}
library(ggplot2)
ggplot(mtcars, aes(x=mpg,y=wt,col=am))+ geom_point()
```


(5)  b. what will happen if change the colour of points use col=as.factor(am) when constructing aesthetic mappings
   

```{r,echo=T,eval=T}
library(ggplot2)
ggplot(mtcars, aes(x=mpg,y=wt,col=as.factor(am)))+ geom_point()
```

